FMA: A Dataset For Music Analysis

### 2017-04-18 fma.tex
reduce size

% PTB 19/3/3, MNIST 60/10, ImageNet 1200/50/100 --> ratio ~6-12
An 80/10/10\% split into training, validation and test sets is proposed to make research on the FMA reproducible. The training and validation sets should be merged if cross-validation is used instead.
Below are the constraints we followed:
% Data was stratified according to the following criteria: ground truth, artist and times filters
\begin{enumerate}
	\item Stratified sampling was used to preserve the percentage of tracks per genre. This is important for minority genres.
	\item An artist filter was used, i.e. an artist was forced to appear in one set only. %All songs from a given artist either appear in train, validation or test, never in two of them.
	%\item Stratified sampling with a time filter, i.e. for each genre using the earlier songs in the training set, and the later releases in the validation and test sets.
	\item Artists with lots of songs were distributed between the sets. %The three sets were alternatively filled in descending order of the count of artist songs. 
\end{enumerate}
The above constraints are satisfied for all subsets, and a track is assigned to the same split across all of them.\footref{creation}

@@

\tabref{tab:mgr} reports classification accuracies for problem 2 with 9 different mainstream feature sets and some combinations as well as 4 standard classifiers using scikit-learn, version 0.18.1 \cite{scikit-learn}. Specifically, we employed linear regression (LR) with an $L^2$ penalty, k-nearest neighbors (kNN) with $k=200$, support vector machines (SVM) with a radial basis function (RBF) kernel and a multilayer perceptron (MLP) with 100 hidden neurons. All classifiers were tested with otherwise default settings.\footnote{See \texttt{baselines.ipynb} for all details.} Reported accuracies should not be taken as the state-art-of-the-art but rather as a lower-bound and an indication of the task's difficulty. Moreover, the developed code can serve as a reference and is easily modified to accommodate other features and classifiers.

@@

In a \href{https://freemusicarchive.org/member/cheyenne_h/blog/FMA_Dataset_for_Researchers}{blog post about this dataset}, Cheyenne Hohman, the Director at the Archive, wrote that ''by embracing the some rights reserved philosophy of Creative Commons, artists are not only making their music available for the public to listen to, but also for educational and research applications``.
Let's hope for a future where sharing is first and researchers feed open platforms with their algorithms while they feed us with data.
% Foster usage of CC and tighter interplay / integration between artists, platforms, users and researchers.

>>>>

% PTB 19/3/3, MNIST 60/10, ImageNet 1200/50/100 --> ratio ~6-12
An 80/10/10\% split into training, validation and test sets is proposed to make research on the FMA reproducible. The training and validation sets should be merged if cross-validation is used instead.
Below are the constraints we followed:
% Data was stratified according to the following criteria: ground truth, artist and times filters
\begin{enumerate}
	\item Stratified sampling was used to preserve the percentage of tracks per genre. This is important for minority genres.
	\item An artist filter was used, i.e. an artist was forced to appear in one set only. %All songs from a given artist either appear in train, validation or test, never in two of them.
	%\item Stratified sampling with a time filter, i.e. for each genre using the earlier songs in the training set, and the later releases in the validation and test sets.
	\item Artists with lots of tracks were allocated across sets. %The three sets were alternatively filled in descending order of the count of artist songs.
\end{enumerate}
The above constraints are satisfied for all subsets, and a track is assigned to the same split across all of them.\footref{creation}

@@

\tabref{tab:mgr} reports accuracies for problem 2 with 9 mainstream feature sets and some combinations as well as 4 standard classifiers using scikit-learn, version 0.18.1 \cite{scikit-learn}. Specifically, we employed linear regression (LR) with an $L^2$ penalty, k-nearest neighbors (kNN) with $k=200$, support vector machines (SVM) with a radial basis function (RBF) kernel and a multilayer perceptron (MLP) with 100 hidden neurons. All classifiers were tested with otherwise default settings.\footnote{See \texttt{baselines.ipynb} for all details.} Reported performance should not be taken as the state-of-the-art but rather as a lower-bound and an indication of the task's difficulty. Moreover, the developed code can serve as a reference and is easily modified to accommodate other features and classifiers.

@@

In a \href{https://freemusicarchive.org/member/cheyenne_h/blog/FMA_Dataset_for_Researchers}{post about the dataset}, Cheyenne Hohman, the Director at the Archive, wrote that ''by embracing the
~\ldots~%some rights reserved
philosophy of Creative Commons, artists are not only making their music available for the public to listen to, but also for educational and research applications``.
Let's hope for a future where sharing is first and researchers feed open platforms with algorithms while they feed us with data.
% Foster usage of CC and tighter interplay / integration between artists, platforms, users and researchers.
